One-dimensional Classical Gas in a Harmonic Trap with Repulsive Interaction

### 2017-12-01 draft_04.tex
edited first (preparatory) section

@@

\caption{N=50,F0=100,E=50000. Upper(lower) five pictures are snapshot of the configuration of the cloud in the stationary(rotating) frame at t=$\frac{1}{5}T$, $\frac{2}{5}T$, $\frac{3}{5}T$, $\frac{4}{5}T$, $T$ respectively.}
\label{fig:Breathingfrequency2_0}
\end{figure*}

>>>>

\subsection{Phase space snapshots}

\caption{N=50,F0=100,E=50000. Upper(lower) five pictures are snapshot of the configuration of the
  cloud in the stationary(rotating) frame at t=$\frac{1}{5}T$, $\frac{2}{5}T$, $\frac{3}{5}T$,
  $\frac{4}{5}T$, $T$ respectively.
WHAT IS T?
}
\label{fig:Breathingfrequency2_0}
\end{figure*}

A very useful way to visualize the state and evolution of the gas is to plot the position and
momentum of each particle, i.e., to plot the locations of the particles in the single-particle phase
space.  This will be useful for visuualizing both the breathing mode and relaxation.

Figures \ref{fig:Breathingfrequency2_0} and \ref{fig:Breathingfrequency2_1} show such phase space
snapshots.

@@
